SBAT: A Simple Browser-based Annotation Tool with Interactive UI and Github Support

### 2024-08-17 paper/main.tex
add option button & update paper outline

% This is used in the PDF meta data
\title{SBAT: A Simple Browser-based Annotation Tool}
\author{Jia Sheng}
\date{\today}

@@

\hrule
\vspace{0.6cm}
{\bfseries\huge
SBAT: A Simple Browser-based Annotation Tool
}\\[1cm] 
\hrule
\vspace*{.05\textheight}

@@

\section{Introduction}
\begin{enumerate}
\item Reason to make this tool: \\
large annotation projects involve many annotators\\
a centrally managed tool needed\\
\item limitation of current annotation tool:\\ 
needs to be hosted on a server\\
offline version needs installation\\
\item introduce SBAT, a browser-based tool for text annotation, can be combined well with github
\end{enumerate}
\section{Related Work}
\begin{enumerate}
\item brat
\item brat-frontend-editor
\item sbat old version by Charlotte
\end{enumerate}
\section{Features}
\begin{enumerate}
\item High-quality Annotation Visualisation and intuitive annotation interface from Brat
\item web interface, no need to register
\item import and export annotations through ui from github
\end{enumerate}
\section{Implementation}
\begin{enumerate}
\item annotation ui from brat
\item static web app hosted on github pages, no need of server
\item github API for reading and writing annotation files
\end{enumerate}

>>>>

% This is used in the PDF meta data
\title{SBAT: A Simple Browser-based Annotation Tool with Interactive UI and Github Support}
\author{Jia Sheng}
\date{\today}

@@

\hrule
\vspace{0.6cm}
{\bfseries\LARGE
SBAT: A Simple Browser-based Annotation Tool with Interative UI and Github Support
}\\[1cm]
\hrule
\vspace*{.05\textheight}

@@

\section{Introduction}
This paper introduces a SBAT, a light-weighted and easy-to-use web annotation tool. Although there are already various apps developed for the purpose of text annotation, they often required to be hosted on a server, which increases the threshold of usage. In comparison, SBAT is developed to be used in a web UI without need of registration or a dedicated server, while still keeping the necessary functions of the heavier annotation tools.
\begin{enumerate}
\item 
Motivation: \\
Easy to use for smaller projects, no budget for a server\\
large annotation projects involve many annotators\\
a centrally managed tool needed\\
\item limitation of current annotation tool:\\ 
needs to be hosted on a server\\
offline version needs installation\\
heavy\\
\item introduce SBAT, a browser-based tool for text annotation, can be combined well with github
\end{enumerate}
\section{Related Work}
\begin{enumerate}
\item brat
\item brat-frontend-editor
\item sbat old version by Charlotte
\item ud-annotatrix
\item inception
\end{enumerate}
\section{Features}
\begin{enumerate}
\item High-quality Annotation Visualisation and intuitive annotation interface from Brat
\item web interface, no need to register
\item import and export annotations through ui from github
\end{enumerate}
\section{Implementation}
\begin{enumerate}
\item annotation ui from brat
\item static web app hosted on github pages, no need of server, no server-side configuration, light-weighted
\item github API for reading and writing annotation files
\end{enumerate}
